---
title: "simpleRegress"
author: "Jaci Heckman"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model WEIGHT ~ NECK  this is an example  

```{r}
simp <- lm(WEIGHT~NECK,data=bears)
plot(WEIGHT~NECK,data=bears)
abline(simp)
summary.lm(simp)
```


## Compare all models that predict WEIGHT other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

```{r}
simp <- lm(WEIGHT~AGE,data=bears)
plot(WEIGHT~AGE,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
simp <- lm(WEIGHT~HEADLEN,data=bears)
plot(WEIGHT~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
simp <- lm(WEIGHT~HEADWTH,data=bears)
plot(WEIGHT~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
simp <- lm(WEIGHT~CHEST,data=bears)
plot(WEIGHT~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
simp <- lm(WEIGHT~LENGTH,data=bears)
plot(WEIGHT~LENGTH,data=bears)
abline(simp)
summary.lm(simp)
```
  
  
The Summary Information:
This is ordered from largest to greatest based on the RSE output. 

1)    NECK: ADJUSTED R-SQUARED 
2)    LENGTH: ADJUSTED R-SQUARED  
3)    HEADLEN: ADJUSTED R-SQUARED 
4)    HEADWTH: ADJUSTED R-SQUARED 
5)    CHEST: ADJUSTED R-SQUARED 
6)    AGE: ADJUSTED R-SQUARED 



